Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Add figure TODO
Write some captions and add caption TODOs

\begin{figure}[t]
  \centering
  \includegraphics[width=0.95\textwidth]{../figures/shepard-rotation.png}
  \caption{Classic mental rotation task from \cite{Shepard1971}.}
  \label{fig:mental-rotation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{Rotated shapes and corresponding similarities.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/li_regression.pdf}
    \caption{Na\"ive model}
    \label{fig:li}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/vm_regression.pdf}
    \caption{Parametric model}
    \label{fig:vm}
  \end{subfigure}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{Nonparametric model}
  \label{fig:bq}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/model_rotations.pdf}
  \caption{Model rotations}
  \label{fig:rotations}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/Z_accuracy.pdf}
  \caption{Accuracy in estimating $Z$.}
  \label{fig:accuracy}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.95\textwidth]{../figures/shepard-rotation.png}
  \caption{\textbf{Classic mental rotation task}. Participants in
    \cite{Shepard1971} saw stimuli such as these, and judged whether
    each pair of shapes was the same shape in two different
    orientations, or two different shapes. \textbf{A} shows a ``plane
    rotation'', \textbf{B} shows a ``depth rotation'', and \textbf{C}
    shows two distinct objects. \TODO{include Shepard results, too?}}
  \label{fig:mental-rotation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{\textbf{Rotated shapes and their similarity.}  \textbf{(a)}
    An example stimulus in which the shapes differ only by a
    rotation. All stimuli consist of five vertices centered around the
    origin, and four edges which create a closed loop from the
    vertices. \textbf{(b)} The approximate likelihood (similarity) of
    $X_b$ given $X_R$, where $X_R$ is a rotation of $X_a$ by the angle
    $R$. The true angle of rotation between $X_a$ and $X_b$ is
    slightly greater than $\pi$, corresponding to the global maximum
    in the likelihood function.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/li_regression.pdf}
    \caption{Na\"ive model}
    \label{fig:li}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/vm_regression.pdf}
    \caption{Parametric model}
    \label{fig:vm}
  \end{subfigure}
  \caption{\TODO{}}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{\textbf{Nonparametric model.} \TODO{}}
  \label{fig:bq}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/model_rotations.pdf}
  \caption{\textbf{Model rotations.} \TODO{}}
  \label{fig:rotations}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/Z_accuracy.pdf}
  \caption{\textbf{Accuracy in estimating $Z$.} \TODO{} \TODO{use
      different markers for $h_0$ and $h_1$ points}}
  \label{fig:accuracy}
\end{figure}
